---
title: Explore a package's datasets
author: Adam Gruer
date: '2018-02-26'
slug: explore-a-packages-datasets
draft: true
categories: []
tags: []
---

Thanks to Bo Peng for asking the question and Prof. Brian Ripley for answering it
https://stat.ethz.ch/pipermail/r-help/2003-April/031666.html
Bo is possibly https://twitter.com/bo_p

* use `library(package_name)` to attach the package to the search list

```{r attach-package}
library(MASS)
library(magrittr)
```
* use `search()` to view a list of attached packages
```{r list-attached-packages}
search()
```


* use `ls(name_of_element_in_search_list)` to return a character vector of all objects in the package environment 
* todo map over all packages and require package then mget

```{r}


package_objects <- ls("package:MASS")
length(package_objects)
set.seed(42)
sample(package_objects, 10)



set.seed(42)
sample_list <- sample(package_objects, 5) %>%  
  mget( as.environment("package:MASS"))
sample_list
purrr::map_chr(sample_list, class) 

head(sample_list$topo)

 data(package = c("MASS","lattice"))$results[,c("Package","Item","Title")] %>% as.data.frame(stringsAsFactors = FALSE) 
 
 
  data(package = .packages(TRUE) )$results[,c("Package","Item","Title")] %>% as.data.frame(stringsAsFactors = FALSE)
 
  
 mapply(`+`, 1:6, 11:16, SIMPLIFY = FALSE)








```


